---
name: Samuel Chagas de Assis
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BCom(Hons), BSc
address: Campinas, São Paulo - Brazil
#profilepic: samuelphoto.jpg
email: samuel.achagas98@gmail.com
www: chagas98.github.io
github: chagas98
linkedin: samuelchagass
position: Biotechnologist - Computational Biologist
#twitter: mitchoharawild
headcolor: 2983f3

output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

---

# About me
\newcommand\tab[1][1cm]{\hspace*{#1}}
\begingroup
\fontsize{10}{12}\selectfont
\tab[1cm]I'm a computational biologist fascinated by understanding the molecular biodiversity and mechanisms. I have experience with workflow development in Python and R, molecular dynamics simulations data analysis, and immunogenetics. Currently, my work focuses on workflow development through documentation, automation, and reproducibility. I’m an intern researcher at the Computational Biocatalysis Group at LNBR/CNPEM in Brazil, where I work with specific Carbohydrate-Active Enzymes for microbiome and structural biology research projects using biomolecular modeling data and biochemical interpretation. When I have some time, I enjoy to draw molecular scientific illustrations and cooking plant-based recipes. 

\endgroup

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
 "Bachelor in Biotechnology", "2018-2024", "Federal University of Latin-American Integration (UNILA)", "Foz do Iguaçu, Brazil",
 "Electrical Technician", "2013-2017", "Liberato Salzano Vieira da Cunha Foudation", "Novo Hamburgo, Brazil"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Experience

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Computational Biocatalysis Intern", "Feb 2023 - Present", "Brazilian Center for Research in Energy and Materials (CNPEM)", "Campinas, São Paulo",
  c("I have performed data analysis of several molecular dynamics simulations, primarily using Python and Shell scripting compatible with SLURM HPC environment. The main goal are new insights about molecular mechanisms from new Carbohydrate-Active enzyme families.", "| Gromacs | SLURM/HPC | Python/MDAnalysis | Python/Autodock Vina | Conda/Bioconda | Pymol/VMD |")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Freelancer - Jr Data Analyst", "Oct 2022 - Feb 2023", "SporeData Inc.", "Remote",
  c("Worked as a freelancer on healthcare data projects, performing ETL, cohort generation, data visualization, clinical study reports, and statistical analyses.", "| R/Tidyverse | RStats | RMarkdown | Cloud/N3C |")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Undergraduate Researcher", "Aug 2020 - Mar 2023", "Medical Genetics Lab - UNILA", "Foz do Iguaçu, Paraná",
  c("I have performed DNA sequencing and HLA-B analysis of COVID-19 patients, gathering clinical and genomic data, along with HLA-epitopes binding affinities from computational predictions, to study the mutational landscape of SARS-CoV-2 variants in Foz do Iguaçu. I worked in a Nextflow pipeline to collect, transform and visualize missense mutations affecting HLA-apitopes.", "| Missense mutation analyses | GISAID | Nextflow | Bash | Python | R | Sanger Sequencing/Wet Lab | netMHCpan4.1 |")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "DryLab Coordinator", "Jan 2020 - Dez 2021", "International Genetically Engineered Machine Competition (iGEM)", "Foz do Iguaçu, Paraná",
  c("", "| system biology modeling | Python/Scipy | Python/NUPACK | R/ggplot2 | ODEs/Modeling |")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Undergraduate Researcher", "Jun 2018 - Dez 2019", "Microbiology and Biochemical Lab - UNILA", "Foz do Iguaçu, Paraná",
  c("", "|  |")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

# Habilidades e Qualificações

\begingroup
\fontsize{10}{12}\selectfont

* Linguagens de Programação: R, Python e Bash
* \textit{Markup}: RMarkdown e HTML
* Gerenciamento: Git/GitHub, GitHub Actions, Slurm
* Sistemas UNIX/Linux


\endgroup


```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Undergraduate Researcher", "Jun 2018 - Dez 2019", "Microbiology and Biochemical Lab - UNILA", "Foz do Iguaçu, Paraná", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

# Prêmios

```{r}
tribble(
  ~Year, ~Type,
  2022, "Primeiro Lugar. Menção Honrosa na área de Ciências da Saúde no XI EICTI - UNILA",
  2021, "Medalha de Ouro e Nomeação de Melhor Projeto de Nova Aplicação e Práticas Humanas na \\textit{International Genetically Engineering Machine Competition} (iGEM)",
  2020, "Melhor Projeto de Escolha do Público no V Curso de Verão de Engenharia de Máquinas Biológicas - UFMG",
  2020, "Melhor Apresentação no V Curso de Verão de Engenharia de Máquinas Biológicas - UFMG",
  2019, "Primeiro Lugar. Menção Honrosa na área de Tecnologia e Produção no VII SEUNI - UNILA",
  2016, "Menção Honrosa UNESCO pelo Projeto de Relevância Social na Conferência Internacional de Ciência e Tecnologia de Nível Médio - MOSTRATEC/UNESCO",
  
  
) %>% 
  brief_entries(
    Type,
    Year, .protect = FALSE)
```

# Publicações

\begingroup
\fontsize{10}{12}\selectfont

* **De Assis**, S.C., Morgado, D.L., Scheidt, D.T., De Souza, S.S., Cavallari, M.R., Ando , O.H.J., Carrilho, E. (2023). Review of Bacterial Nanocellulose-Based Electrochemical Biosensors: Functionalization, Challenges, and Future Perspectives. *MDPI Biosensors*, 13. [https://doi.org/10.3390/bios13010142](https://doi.org/10.3390/bios13010142)


\endgroup

