---
name: Samuel Chagas de Assis
date: "`r format(Sys.time(), '%B %Y', us <- Sys.setlocale('LC_TIME','C'))`"
qualifications: BCom(Hons), BSc
address: Campinas, São Paulo - Brazil
#profilepic: samuelphoto.jpg
email: samuel.assis@lnbio.cnpem.br
www: chagas98.github.io
github: chagas98
linkedin: samuelchagass
position: Computational Biologist Researcher
#twitter: mitchoharawild
headcolor: 2983f3

output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

---

# About me
\newcommand\tab[1][1cm]{\hspace*{#1}}
\begingroup
\fontsize{10}{12}\selectfont
\tab[1cm] Master’s student in Computational Biology and Pharmaceutical Sciences at the Brazilian Center for Research in Energy and Materials (CNPEM) and the University of Campinas (UNICAMP), currently conducting research with the Protein Design Group. My work focuses on applying and developing computational methods grounded in geometric deep learning to investigate protein–protein interactions. I am developing classification models using public immunological datasets, exploring graph-based representations and architectures, and leveraging model interpretability to uncover mechanistic insights into molecular recognition.

\endgroup

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "MSc in Computational Biology and Pharmaceutical Sciences", "2025-now", "Brazilian Center for Research in Energy and Materials (CNPEM) | State University of Campinas (UNICAMP)", "Campinas/São Paulo, Brazil",
 "BSc in Biotechnology", "2018-2024", "Federal University of Latin-American Integration (UNILA)", "Foz do Iguaçu, Brazil") %>% 
  detailed_entries(Degree, Year, Institution, Where, .protect = FALSE)
```

# Experience

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Computational Biocatalysis Intern", "Feb 2023 - Dec 2024", "Brazilian Center for Research in Energy and Materials (CNPEM)", "Campinas, São Paulo",
  c("I performed  several molecular dynamics simulations and large-scale data analysis on HPC environment. The main goal are new insights about molecular mechanisms from new Carbohydrate-Active enzymes, which benefits the experimental team for mutation screening and activity assays.")) %>% 
  detailed_entries(Position, Year, Institution, Where, Why, .protect = FALSE)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Freelancer - Jr Data Analyst", "Oct 2022 - Feb 2023", "SporeData Inc.", "Remote",
  c("Worked as a freelancer on healthcare data projects, performing ETL, cohort generation, data visualization, clinical study reports, and statistical analyses. ")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why, .protect = FALSE)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Undergraduate Researcher", "Aug 2020 - Mar 2023", "Medical Genetics Lab - UNILA", "Foz do Iguaçu, Brazil",
  c("I conducted DNA sequencing and HLA-B genotyping of COVID‑19 patients in Foz do Iguaçu, integrating clinical and genomic data with computational predictions of HLA‑epitope binding affinities. The study aimed to explore the mutational landscape of SARS‑CoV‑2 variants and their potential impact on immune recognition.")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why, .protect = FALSE)
```

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "DryLab Coordinator", "Jan 2020 - Dez 2021", "International Genetically Engineered Machine Competition (iGEM)", "Paris, France",
  c("As the Head of DryLab at the iGEM UNILA LatAm Team, I led the development of a kinetic model with parameter optimization. We used an Ordinary Differential Equations (ODEs) framework coupled with sensitivity analysis to evaluate and optimized the performance of our synthetic genetic circuit.")
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why, .protect = FALSE)
```


# Skills

```{r}
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Python | Bash | R", "", "Programming", "", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)

tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "PyTorch | PyTorch Geometric | NumPy | Scikit-learn |", "", "Packages", "", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)


tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Nextflow", "", "Workflow", "", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)

tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Docker | Singularity", "", "Container", "", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)

tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Git | Github | Slurm | R/Shiny | Python/Flask", "", "Tools", "", c()
) %>% 
  detailed_entries(Position, Year, Institution, Where, Why)
```

# Accomplishments

```{r}
tribble(
  ~Year, ~Type,
  2022, "1st Place. Honorable Mention in Health Science at XI EICTI, UNILA",
  2021, "Gold Medal at International Genetically Engineering Machine Competition - iGEM",
  2020, "Best Public Choice Project at the V Biological Machines Engineering Summer Program - UFMG",
  2020, "Best Presentation Award at the V Biological Machine Engineering Summer Program - UFMG",
  2019, "1st Place. Honorable Mention in Technology and Production at VII SEUNI - UNILA",
) %>% 
  brief_entries(
    Type,
    Year, .protect = FALSE)
```

